---
title: "GOslim"
author: "jillashey"
date: "10/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages 
library(readr)
library(arsenal)
library(tidyverse)
```

This code uses GO term annotation generated in Nov-Dec 2021 and Jan 2022

# Read in go slim info
```{r}
go.slim <- read_csv("Output/GOSeq/GO-GOslim.csv")
colnames(go.slim) <- c("GO.IDs", "GO.Term", "GO.Slim.Term", "Cat") #rename columns
```

The specific csv I used was obtained from HP's Geoduck_Meth [repo](https://github.com/hputnam/Geoduck_Meth/blob/master/RAnalysis/Data/20210407_map2MGIslim.csv). It was used in this [script](https://github.com/hputnam/Geoduck_Meth/blob/master/RAnalysis/Scripts/GM.Rmd#L1648) and was accessed on 20210407 from [here](http://www.informatics.jax.org/gotools/data/input/map2MGIslim.txt). 

## Florida 

### Acerv
```{r}
# Read in acerv DEG GO terms 
acerv.go <- read.csv("Output/GOSeq/acerv/acerv_sub_ByTreatment_GO.terms_20211104.csv", header = T)
acerv.go <- select(acerv.go, c("gene_id", "category", "term", "ontology", "over_represented_pvalue", "log2FoldChange", "padj", "Treatment_Compare")) # can add treatment compare if interested 
colnames(acerv.go)[2] <-"GO.IDs"
acerv.go$Species <- "A.cervicornis"
acerv.go$Site <- "Florida"
acerv.go <- unique(acerv.go)
length(unique(acerv.go$GO.IDs)) # 366 unique GO terms 

# Merge w/ GO slim and subset by ontology
acerv.go.slim <- merge(acerv.go, go.slim, by="GO.IDs", all = TRUE)
#write.csv(acerv.go.slim, "Output/GOSeq/acerv/acerv.go.slim_20220208.csv")

acerv.go.slim.BP <- subset(acerv.go.slim, ontology == "BP")
acerv.go.slim.BP <- unique(acerv.go.slim.BP)
length(unique(acerv.go.slim.BP$GO.IDs)) # 278 unique BP GO terms 
#write.csv(acerv.go.slim.BP, "Output/GOSeq/acerv/acerv.go.slim.BP_20220208.csv")
acerv.go.slim.BP_uniq <- acerv.go.slim.BP %>% select("GO.IDs")
acerv.go.slim.BP_uniq <- unique(acerv.go.slim.BP_uniq)
#write.csv(acerv.go.slim.BP_uniq, "Output/GOSeq/acerv/acerv.go.slim.BP_unique_20220418.csv")

acerv.go.slim.CC <- subset(acerv.go.slim, ontology == "CC")
acerv.go.slim.CC <- unique(acerv.go.slim.CC)
length(unique(acerv.go.slim.CC$GO.IDs)) # 34 unique CC GO terms 
#write.csv(acerv.go.slim.CC, "Output/GOSeq/acerv/acerv.go.slim.CC_20220208.csv")
acerv.go.slim.CC_uniq <- acerv.go.slim.CC %>% select("GO.IDs")
acerv.go.slim.CC_uniq <- unique(acerv.go.slim.CC_uniq)
#write.csv(acerv.go.slim.CC_uniq, "Output/GOSeq/acerv/acerv.go.slim.CC_unique_20220418.csv")

acerv.go.slim.MF <- subset(acerv.go.slim, ontology == "MF")
acerv.go.slim.MF <- unique(acerv.go.slim.MF)
length(unique(acerv.go.slim.MF$GO.IDs)) # 54 unique MF GO terms 
#write.csv(acerv.go.slim.MF, "Output/GOSeq/acerv/acerv.go.slim.MF_20220208.csv")
acerv.go.slim.MF_uniq <- acerv.go.slim.MF %>% select("GO.IDs")
acerv.go.slim.MF_uniq <- unique(acerv.go.slim.MF_uniq)
#write.csv(acerv.go.slim.MF_uniq, "Output/GOSeq/acerv/acerv.go.slim.MF_unique_20220418.csv")

## In Excel, I take the unique go term files, remove excess rows/cols so its just a list of GO terms. Then plotted using this website: https://bioinformatics.psb.ugent.be/cgi-bin/liste/Venn/calculate_venn.htpl. can't figure out how to do it in R
```

### Mcav
```{r}
# Read in Mcav DEG GO terms 
mcav.go <- read.csv("Output/GOSeq/mcav/mcav_ByTreatment_GO.terms_20211109.csv", header = T)
mcav.go <- select(mcav.go, c("gene_id", "category", "term", "ontology", "over_represented_pvalue", "log2FoldChange", "padj", "Treatment_Compare")) # can add treatment compare if interested 
colnames(mcav.go)[2] <-"GO.IDs"
mcav.go$Species <- "M.cavernosa"
mcav.go$Site <- "Florida"
mcav.go <- unique(mcav.go)
length(unique(mcav.go$GO.IDs)) # 220 unique GO terms 

# Merge w/ GO slim and subset by ontology
mcav.go.slim <- merge(mcav.go, go.slim, by="GO.IDs", all = TRUE)
#write.csv(mcav.go.slim, "Output/GOSeq/mcav/mcav.go.slim_20220208.csv")

mcav_all.go.slim.BP <- subset(mcav.go.slim, ontology == "BP")
mcav_all.go.slim.BP <- unique(mcav_all.go.slim.BP)
length(unique(mcav_all.go.slim.BP$GO.IDs)) # 158 unique BP GO terms 
#write.csv(mcav_all.go.slim.BP, "Output/GOSeq/mcav/mcav.go.slim.BP_20220208.csv")
mcav_all.go.slim.BP_uniq <- mcav_all.go.slim.BP %>% select("GO.IDs")
mcav_all.go.slim.BP_uniq <- unique(mcav_all.go.slim.BP_uniq)
write.csv(mcav_all.go.slim.BP_uniq, "Output/GOSeq/mcav/mcav.go.slim.BP_unique_20220418.csv")

mcav_all.go.slim.CC <- subset(mcav.go.slim, ontology == "CC")
mcav_all.go.slim.CC <- unique(mcav_all.go.slim.CC)
length(unique(mcav_all.go.slim.CC$GO.IDs)) # 21 unique BP GO terms 
#write.csv(mcav_all.go.slim.CC, "Output/GOSeq/mcav/mcav.go.slim.CC_20220208.csv")
mcav_all.go.slim.CC_uniq <- mcav_all.go.slim.CC %>% select("GO.IDs")
mcav_all.go.slim.CC_uniq <- unique(mcav_all.go.slim.CC_uniq)
write.csv(mcav_all.go.slim.CC_uniq, "Output/GOSeq/mcav/mcav.go.slim.CC_unique_20220418.csv")

mcav_all.go.slim.MF <- subset(mcav.go.slim, ontology == "MF")
mcav_all.go.slim.MF <- unique(mcav_all.go.slim.MF)
length(unique(mcav_all.go.slim.MF$GO.IDs)) # 39 unique BP GO terms 
#write.csv(mcav_all.go.slim.MF, "Output/GOSeq/mcav/mcav.go.slim.MF_20220208.csv")
mcav_all.go.slim.MF_uniq <- mcav_all.go.slim.MF %>% select("GO.IDs")
mcav_all.go.slim.MF_uniq <- unique(mcav_all.go.slim.MF_uniq)
write.csv(mcav_all.go.slim.MF_uniq, "Output/GOSeq/mcav/mcav.go.slim.MF_unique_20220418.csv")

## In Excel, I take the unique go term files, remove excess rows/cols so its just a list of GO terms. Then plotted using this website: https://bioinformatics.psb.ugent.be/cgi-bin/liste/Venn/calculate_venn.htpl. can't figure out how to do it in R
```

### Ofav
```{r}
# Read in Ofav DEG GO terms 
ofav.go <- read.csv("Output/GOSeq/ofav/ofav_ByTreatment_GO.terms_20220111.csv", header = T)
ofav.go <- select(ofav.go, c("gene_id", "category", "term", "ontology", "over_represented_pvalue", "log2FoldChange", "padj", "Treatment_Compare")) # can add treatment compare if interested 
colnames(ofav.go)[2] <-"GO.IDs"
ofav.go$Species <- "O.faveolata"
ofav.go$Site <- "Florida"
ofav.go <- unique(ofav.go)
length(unique(ofav.go$GO.IDs)) # 39 unique GO terms 

# Merge w/ GO slim and subset by ontology
ofav.go.slim <- merge(ofav.go, go.slim, by="GO.IDs", all = TRUE)
#write.csv(ofav.go.slim, "Output/GOSeq/ofav/ofav.go.slim_20220208.csv")

ofav_all.go.slim.BP <- subset(ofav.go.slim, ontology == "BP")
ofav_all.go.slim.BP <- unique(ofav_all.go.slim.BP)
length(unique(ofav_all.go.slim.BP$GO.IDs)) # 27 unique BP GO terms 
#write.csv(ofav_all.go.slim.BP, "Output/GOSeq/ofav/ofav.go.slim.BP_20220208.csv")
ofav_all.go.slim.BP_uniq <- ofav_all.go.slim.BP %>% select("GO.IDs")
ofav_all.go.slim.BP_uniq <- unique(ofav_all.go.slim.BP_uniq)
write.csv(ofav_all.go.slim.BP_uniq, "Output/GOSeq/ofav/ofav_all.go.slim.BP_uniq_20220418.csv")

ofav_all.go.slim.CC <- subset(ofav.go.slim, ontology == "CC")
ofav_all.go.slim.CC <- unique(ofav_all.go.slim.CC)
length(unique(ofav_all.go.slim.CC$GO.IDs)) # 3 unique BP GO terms 
#write.csv(ofav_all.go.slim.CC, "Output/GOSeq/ofav/ofav.go.slim.CC_20220208.csv")
ofav_all.go.slim.CC_uniq <- ofav_all.go.slim.CC %>% select("GO.IDs")
ofav_all.go.slim.CC_uniq <- unique(ofav_all.go.slim.CC_uniq)
write.csv(ofav_all.go.slim.CC_uniq, "Output/GOSeq/ofav/ofav_all.go.slim.CC_uniq_20220418.csv")

ofav_all.go.slim.MF <- subset(ofav.go.slim, ontology == "MF")
ofav_all.go.slim.MF <- unique(ofav_all.go.slim.MF)
length(unique(ofav_all.go.slim.MF$GO.IDs)) # 9 unique BP GO terms 
#write.csv(ofav_all.go.slim.MF, "Output/GOSeq/ofav/ofav.go.slim.MF_20220208.csv")
ofav_all.go.slim.MF_uniq <- ofav_all.go.slim.MF %>% select("GO.IDs")
ofav_all.go.slim.MF_uniq <- unique(ofav_all.go.slim.CC_uniq)
write.csv(ofav_all.go.slim.MF_uniq, "Output/GOSeq/ofav/ofav_all.go.slim.MF_uniq_20220418.csv")

## In Excel, I take the unique go term files, remove excess rows/cols so its just a list of GO terms. Then plotted using this website: https://bioinformatics.psb.ugent.be/cgi-bin/liste/Venn/calculate_venn.htpl. can't figure out how to do it in R
```

## Hawaii

### Mcap 
```{r}
# Read in mcap DEG GO terms
mcap.go <- read.csv("Output/GOSeq/mcap/mcap_ByTreatment_GO.terms_20220417.csv", header = T)
mcap.go <- select(mcap.go, c("gene_id", "category", "term", "ontology", "over_represented_pvalue", "log2FoldChange", "padj", "Treatment_Compare")) # can add treatment compare if interested 
colnames(mcap.go)[2] <-"GO.IDs"
mcap.go$Species <- "M.capitata"
mcap.go$Site <- "Hawaii"
mcap.go <- unique(mcap.go)
length(unique(mcap.go$GO.IDs)) # 343 unique GO terms 

# Merge w/ GO slim and subset by ontology
mcap.go.slim <- merge(mcap.go, go.slim, by="GO.IDs", all = TRUE)
#write.csv(mcap.go.slim, "Output/GOSeq/mcap/mcap.go.slim_20220417.csv")

mcap_all.go.slim.BP <- subset(mcap.go.slim, ontology == "BP")
mcap_all.go.slim.BP <- unique(mcap_all.go.slim.BP)
length(unique(mcap_all.go.slim.BP$GO.IDs)) # 237 unique BP GO terms 
#write.csv(pacuta_all.go.slim.BP, "Output/GOSeq/mcap/mcap.go.slim.BP_20220417.csv")
mcap_all.go.slim.BP_uniq <- mcap_all.go.slim.BP %>% select("GO.IDs")
mcap_all.go.slim.BP_uniq <- unique(mcap_all.go.slim.BP_uniq)
write.csv(mcap_all.go.slim.BP_uniq, "Output/GOSeq/mcap/mcap_all.go.slim.BP_uniq_20220418.csv")

mcap_all.go.slim.CC <- subset(mcap.go.slim, ontology == "CC")
mcap_all.go.slim.CC <- unique(mcap_all.go.slim.CC)
length(unique(mcap_all.go.slim.CC$GO.IDs)) # 40 unique BP GO terms 
#write.csv(mcap_all.go.slim.CC, "Output/GOSeq/mcap/mcap.go.slim.CC_20220417.csv")
mcap_all.go.slim.CC_uniq <- mcap_all.go.slim.CC %>% select("GO.IDs")
mcap_all.go.slim.CC_uniq <- unique(mcap_all.go.slim.CC_uniq)
write.csv(mcap_all.go.slim.CC_uniq, "Output/GOSeq/mcap/mcap_all.go.slim.CC_uniq_20220418.csv")

mcap_all.go.slim.MF <- subset(mcap.go.slim, ontology == "MF")
mcap_all.go.slim.MF <- unique(mcap_all.go.slim.MF)
length(unique(mcap_all.go.slim.MF$GO.IDs)) # 65 unique BP GO terms 
#write.csv(mcap_all.go.slim.MF, "Output/GOSeq/mcap/mcap.go.slim.MF_20220417.csv")
mcap_all.go.slim.MF_uniq <- mcap_all.go.slim.MF %>% select("GO.IDs")
mcap_all.go.slim.MF_uniq <- unique(mcap_all.go.slim.MF_uniq)
write.csv(mcap_all.go.slim.MF_uniq, "Output/GOSeq/mcap/mcap_all.go.slim.MF_uniq_20220418.csv")

## In Excel, I take the unique go term files, remove excess rows/cols so its just a list of GO terms. Then plotted using this website: https://bioinformatics.psb.ugent.be/cgi-bin/liste/Venn/calculate_venn.htpl. can't figure out how to do it in R
```

### Pacuta 
```{r}
# Read in pacuta DEG GO terms
pacuta.go <- read.csv("Output/GOSeq/pacuta/pacuta_ByTreatment_GO.terms_20220121.csv", header = T)
pacuta.go <- select(pacuta.go, c("gene_id", "category", "term", "ontology", "over_represented_pvalue", "log2FoldChange", "padj", "Treatment_Compare")) # can add treatment compare if interested 
colnames(pacuta.go)[2] <-"GO.IDs"
pacuta.go$Species <- "P.acuta"
pacuta.go$Site <- "Hawaii"
pacuta.go <- unique(pacuta.go)
length(unique(pacuta.go$GO.IDs)) # 532 unique GO terms 

# Merge w/ GO slim and subset by ontology
pacuta.go.slim <- merge(pacuta.go, go.slim, by="GO.IDs", all = TRUE)
#write.csv(pacuta.go.slim, "Output/GOSeq/pacuta/pacuta.go.slim_20220208.csv")

pacuta_all.go.slim.BP <- subset(pacuta.go.slim, ontology == "BP")
pacuta_all.go.slim.BP <- unique(pacuta_all.go.slim.BP)
length(unique(pacuta_all.go.slim.BP$GO.IDs)) # 380 unique BP GO terms 
#write.csv(pacuta_all.go.slim.BP, "Output/GOSeq/pacuta/pacuta.go.slim.BP_20220208.csv")
pacuta_all.go.slim.BP_uniq <- pacuta_all.go.slim.BP %>% select("GO.IDs")
pacuta_all.go.slim.BP_uniq <- unique(pacuta_all.go.slim.BP_uniq)
write.csv(pacuta_all.go.slim.BP_uniq, "Output/GOSeq/pacuta/pacuta_all.go.slim.BP_uniq_20220418.csv")

pacuta_all.go.slim.CC <- subset(pacuta.go.slim, ontology == "CC")
pacuta_all.go.slim.CC <- unique(pacuta_all.go.slim.CC)
length(unique(pacuta_all.go.slim.CC$GO.IDs)) # 25 unique CC GO terms 
#write.csv(pacuta_all.go.slim.CC, "Output/GOSeq/pacuta/pacuta.go.slim.CC_20220208.csv")
pacuta_all.go.slim.CC_uniq <- pacuta_all.go.slim.CC %>% select("GO.IDs")
pacuta_all.go.slim.CC_uniq <- unique(pacuta_all.go.slim.CC_uniq)
write.csv(pacuta_all.go.slim.CC_uniq, "Output/GOSeq/pacuta/pacuta_all.go.slim.CC_uniq_20220418.csv")

pacuta_all.go.slim.MF <- subset(pacuta.go.slim, ontology == "MF")
pacuta_all.go.slim.MF <- unique(pacuta_all.go.slim.MF)
length(unique(pacuta_all.go.slim.MF$GO.IDs)) # 126 unique MF GO terms 
#write.csv(pacuta_all.go.slim.MF, "Output/GOSeq/pacuta/pacuta.go.slim.MF_20220208.csv")
pacuta_all.go.slim.MF_uniq <- pacuta_all.go.slim.MF %>% select("GO.IDs")
pacuta_all.go.slim.MF_uniq <- unique(pacuta_all.go.slim.MF_uniq)
write.csv(pacuta_all.go.slim.MF_uniq, "Output/GOSeq/pacuta/pacuta_all.go.slim.MF_uniq_20220418.csv")

## In Excel, I take the unique go term files, remove excess rows/cols so its just a list of GO terms. Then plotted using this website: https://bioinformatics.psb.ugent.be/cgi-bin/liste/Venn/calculate_venn.htpl. can't figure out how to do it in R
```

### Plob 
```{r}
# Read in plob DEG GO terms
plob.go <- read.csv("Output/GOSeq/plob/plob_ByTreatment_GO.terms_20211106.csv", header = T)
plob.go <- select(plob.go, c("gene_id", "category", "term", "ontology", "over_represented_pvalue", "log2FoldChange", "padj", "Treatment_Compare")) # can add treatment compare if interested 
colnames(plob.go)[2] <-"GO.IDs"
plob.go$Species <- "P.lobata"
plob.go$Site <- "Hawaii"
plob.go <- unique(plob.go)
length(unique(plob.go$GO.IDs)) # 279 unique GO terms 

# Merge w/ GO slim and subset by ontology
plob.go.slim <- merge(plob.go, go.slim, by="GO.IDs", all = TRUE)
#write.csv(plob.go.slim, "Output/GOSeq/plob/plob.go.slim_20220208.csv")

plob_all.go.slim.BP <- subset(plob.go.slim, ontology == "BP")
plob_all.go.slim.BP <- unique(plob_all.go.slim.BP)
length(unique(plob_all.go.slim.BP$GO.IDs)) # 198 unique BP GO terms 
#write.csv(plob_all.go.slim.BP, "Output/GOSeq/plob/plob.go.slim.BP_20220208.csv")
plob_all.go.slim.BP_uniq <- plob_all.go.slim.BP %>% select("GO.IDs")
plob_all.go.slim.BP_uniq <- unique(plob_all.go.slim.BP_uniq)
write.csv(plob_all.go.slim.BP_uniq, "Output/GOSeq/plob/plob_all.go.slim.BP_uniq_20220418.csv")

plob_all.go.slim.CC <- subset(plob.go.slim, ontology == "CC")
plob_all.go.slim.CC <- unique(plob_all.go.slim.CC)
length(unique(plob_all.go.slim.CC$GO.IDs)) # 31 unique CC GO terms 
#write.csv(plob_all.go.slim.CC, "Output/GOSeq/plob/plob.go.slim.CC_20220208.csv")
plob_all.go.slim.CC_uniq <- plob_all.go.slim.CC %>% select("GO.IDs")
plob_all.go.slim.CC_uniq <- unique(plob_all.go.slim.CC_uniq)
write.csv(plob_all.go.slim.CC_uniq, "Output/GOSeq/plob/plob_all.go.slim.CC_uniq_20220418.csv")

plob_all.go.slim.MF <- subset(plob.go.slim, ontology == "MF")
plob_all.go.slim.MF <- unique(plob_all.go.slim.MF)
length(unique(plob_all.go.slim.MF$GO.IDs)) # 50 unique MF GO terms 
#write.csv(plob_all.go.slim.MF, "Output/GOSeq/plob/plob.go.slim.MF_20220208.csv")
plob_all.go.slim.MF_uniq <- plob_all.go.slim.MF %>% select("GO.IDs")
plob_all.go.slim.MF_uniq <- unique(plob_all.go.slim.MF_uniq)
write.csv(plob_all.go.slim.MF_uniq, "Output/GOSeq/plob/plob_all.go.slim.MF_uniq_20220418.csv")

## In Excel, I take the unique go term files, remove excess rows/cols so its just a list of GO terms. Then plotted using this website: https://bioinformatics.psb.ugent.be/cgi-bin/liste/Venn/calculate_venn.htpl. can't figure out how to do it in R
```

I used the unique docs for all the species to make 6-way venn diagram with this [website](https://bioinformatics.psb.ugent.be/webtools/Venn/).


## Combine GO slim terms with all species in single df 
```{r}
# Bind all species df together for GO slim plot 
all.go.slim <- rbind(acerv.go.slim, 
                     mcav.go.slim, 
                     ofav.go.slim,
                     mcap.go.slim,
                     pacuta.go.slim, 
                     plob.go.slim)
write.csv(all.go.slim, "Output/GOSeq/all.go.slim_20220417.csv")

# Plot 
all.go.slim <- na.omit(all.go.slim)
GO.all <- ggplot(all.go.slim, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8),
                     strip.text.x = element_text(size = 8),
                     axis.text = element_text(size = 8))
GO.all
ggsave("Output/Figs/all_GOslim_20220417.pdf", GO.all, width = 40, height = 40, units = c("in"))


# Bind all species df together for BP GO slim plot 
all.go.BP.slim <- rbind(acerv.go.slim.BP, 
                     mcav_all.go.slim.BP, 
                     ofav_all.go.slim.BP,
                     mcap_all.go.slim.BP,
                     pacuta_all.go.slim.BP, 
                     plob_all.go.slim.BP)
write.csv(all.go.BP.slim, "Output/GOSeq/all.go.BP.slim_20220417.csv")

# Plot 
all.go.BP.slim <- na.omit(all.go.BP.slim)
GO.BP.all <- ggplot(all.go.BP.slim, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8),
                     strip.text.x = element_text(size = 8),
                     axis.text = element_text(size = 8))
GO.BP.all
ggsave("Output/Figs/all_GOslim.BP_20220417.pdf", GO.BP.all, width = 40, height = 40, units = c("in"))


# Bind all species df together for CC GO slim plot 
all.go.CC.slim <- rbind(acerv.go.slim.CC, 
                     mcav_all.go.slim.CC, 
                     ofav_all.go.slim.CC,
                     mcap_all.go.slim.CC,
                     pacuta_all.go.slim.CC, 
                     plob_all.go.slim.CC)
write.csv(all.go.CC.slim, "Output/GOSeq/all.go.CC.slim_20220417.csv")

# Plot 
all.go.CC.slim <- na.omit(all.go.CC.slim)
GO.CC.all <- ggplot(all.go.CC.slim, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8),
                     strip.text.x = element_text(size = 8),
                     axis.text = element_text(size = 8))
GO.CC.all
ggsave("Output/Figs/all_GOslim.CC_20220417.pdf", GO.CC.all, width = 40, height = 40, units = c("in"))


# Bind all species df together for MF GO slim plot and merge w/ GO slim terms
all.go.MF.slim <- rbind(acerv.go.slim.MF, 
                     mcav_all.go.slim.MF, 
                     ofav_all.go.slim.MF,
                     pacuta_all.go.slim.MF, 
                     plob_all.go.slim.MF)
write.csv(all.go.MF.slim, "Output/GOSeq/all.go.MF.slim_20220417.csv")

# Plot 
all.go.MF.slim <- na.omit(all.go.MF.slim)
GO.MF.all <- ggplot(all.go.MF.slim, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 8),
                     strip.text.x = element_text(size = 8),
                     axis.text = element_text(size = 8))
GO.MF.all
ggsave("Output/Figs/all_GOslim.MF_20220417.pdf", GO.MF.all, width = 40, height = 40, units = c("in"))
```

Make bar charts for go slim term counts for species, locations, and morphologies - BP only
```{r}
# read in data
all.go.BP.slim <- read.csv("Output/GOSeq/all.go.BP.slim_20220417.csv", header = T)

# Check species names
unique(all.go.BP.slim$Species)
# "A.cervicornis" "M.cavernosa"   "O.faveolata"   "M.capitata"   "P.acuta"       "P.lobata"  

# for this plot, remove "other biological processes",  "other metabolic processes", and NA
#all.go.BP.slim <- subset(all.go.BP.slim, !GO.Slim.Term == "other biological processes" & !GO.Slim.Term == "other metabolic processes")
all.go.BP.slim <- subset(all.go.BP.slim, !GO.Slim.Term == "NA")

# plot by species 
## plotting unique GO terms only - if I plot with all.go.BP.slim, I get duplicate GO slim terms bc its duplicating based on gene id/treatment?
test <- select(all.go.BP.slim, c("GO.IDs", "term", "Species", "GO.Slim.Term"))
test <- unique(test)
test <- na.omit(test)

# count GOslim by species
count_by_group <- test %>%
  dplyr::count(Species, GO.Slim.Term)
count_by_group

# plot
count <- ggplot(count_by_group, aes(fill = Species, y = n, x = GO.Slim.Term)) +
  geom_bar(position = "dodge", 
           stat = "identity", 
           width = 0.9) +
  # geom_text(aes(label = n), 
  #           position = position_dodge(0.9), 
  #           size = 10, 
  #           face = "bold") +
  labs(title="Counts of GO Slim Categories", x ="", y = "Counts") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 65, 
                                   #vjust = 0.5, 
                                   hjust= 1, 
                                   size=60)) + 
  theme(axis.text.y = element_text(size = 60)) +
  theme(axis.title.y = element_text(size = 40)) +
  theme(plot.title = element_text(size = 100, hjust = 0.5)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) + 
  theme(legend.title = element_text(size = 60), 
        legend.key.size = unit(2, "cm"),
        legend.text = element_text(size=60), 
        legend.position = c(0.85, 0.85), 
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.background = element_rect(fill = "white", color = "black")) + 
  scale_fill_manual(values = c("dodgerblue", "goldenrod1", "darkorange1", "seagreen3", "orchid3", "grey"))
count
ggsave("Output/Figs/SpeciesCounts_GOslim.BP_20220417.pdf", count, width = 40, height = 30, units = c("in"))
ggsave("Output/Figs/SpeciesCounts_GOslim.BP_20220417.png", count, width = 40, height = 30, units = c("in"))

# plot by location/sediment type
all.go.BP.slim <- all.go.BP.slim %>% mutate(Location = 
                                              case_when(Species == "A.cervicornis" ~ "Florida", 
                                                        Species == "M.cavernosa" ~ "Florida",
                                                        Species == "O.faveolata" ~ "Florida",
                                                        Species == "M.capitata" ~ "Hawaii",
                                                        Species == "P.acuta" ~ "Hawaii",
                                                        Species == "P.lobata" ~ "Hawaii"))

# count GOslim by location
count_by_location <- all.go.BP.slim %>%
  dplyr::count(Location, GO.Slim.Term)
count_by_location

# plot
count_location_plot <- ggplot(count_by_location, aes(fill = Location, y = n, x = GO.Slim.Term)) +
  geom_bar(position = "dodge", 
           stat = "identity", 
           colour="black",
           width = 0.9,
           size = 2) +
  # geom_text(aes(label = n), 
  #           position = position_dodge(0.9), 
  #           size = 10, 
  #           face = "bold") +
  ylab("GO Term Counts\n") + 
  #ggtitle(label = "Counts of GO Slim Categories by Location") +
  #coord_flip() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 65,
                                   #vjust = 0.5, 
                                   hjust= 1, 
                                   size=80, 
                                   colour = "black"), 
        axis.text.y = element_text(size = 60, colour = "black"),
        axis.title.y = element_text(size = 80, face = "bold"),
        axis.line = element_line(colour = 'black', size = 2),
        plot.title = element_text(size = 100, hjust = 0.5),
        plot.margin = margin(3,3,3,3, "cm")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, 750)) + 
  theme(legend.title = element_text(size = 80), 
        legend.key.size = unit(2, "cm"),
        legend.text = element_text(size=80), 
        legend.position = c(0.85, 0.85), 
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.background = element_rect(fill = "white", color = "black"),
        legend.box.background = element_rect(color="black", size=2)) +
        scale_fill_manual(values = c("chartreuse3", "chocolate2"))
count_location_plot
ggsave("Output/Figs/LocationsCounts_GOslim.BP_20220417.pdf", count_location_plot, width = 49, height = 40, units = c("in"))
ggsave("Output/Figs/LocationsCounts_GOslim.BP_20220417.png", count_location_plot, width = 49, height = 40, units = c("in"))

# plot by morphology type
all.go.BP.slim <- all.go.BP.slim %>% mutate(Morphology = 
                                              case_when(Species == "A.cervicornis" ~ "Branching", 
                                                        Species == "M.cavernosa" ~ "Massive",
                                                        Species == "O.faveolata" ~ "Massive",
                                                        Species == "M.capitata" ~ "Branching",
                                                        Species == "P.acuta" ~ "Branching",
                                                        Species == "P.lobata" ~ "Massive"))

# count GOslim by morphology
count_by_morph <- all.go.BP.slim %>%
  dplyr::count(Morphology, GO.Slim.Term)
count_by_morph

# plot
count_morph_plot <- ggplot(count_by_morph, aes(fill = Morphology, y = n, x = GO.Slim.Term)) +
    geom_bar(position = "dodge", 
           stat = "identity", 
           colour="black",
           width = 0.9,
           size = 2) +
  # geom_text(aes(label = n), 
  #           position = position_dodge(0.9), 
  #           size = 10, 
  #           face = "bold") +
  ylab("GO Term Counts\n") + 
  #ggtitle(label = "Counts of GO Slim Categories by Morphology") +
  #coord_flip() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 65,
                                   #vjust = 0.5, 
                                   hjust= 1, 
                                   size=80, 
                                   colour = "black"), 
        axis.text.y = element_text(size = 60, colour = "black"),
        axis.title.y = element_text(size = 80, face = "bold"),
        axis.line = element_line(colour = 'black', size = 2),
        plot.title = element_text(size = 100, hjust = 0.5),
        plot.margin = margin(3,3,3,3, "cm")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, 775)) + 
  theme(legend.title = element_text(size = 80), 
        legend.key.size = unit(2, "cm"),
        legend.text = element_text(size=80), 
        legend.position = c(0.85, 0.85), 
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.background = element_rect(fill = "white", color = "black"),
        legend.box.background = element_rect(color="black", size=2)) +
        scale_fill_manual(values = c("paleturquoise3", "rosybrown2"))
count_morph_plot
ggsave("Output/Figs/MorphologyCounts_GOslim.BP_20220417.pdf", count_morph_plot, width = 49, height = 40, units = c("in"))
ggsave("Output/Figs/MorphologyCounts_GOslim.BP_20220417.png", count_morph_plot, width = 49, height = 40, units = c("in"))
```

## Make contingency tables (info [here](https://www.datacamp.com/community/tutorials/contingency-tables-r))
```{r}
# By location
tabl1 <- table(all.go.BP.slim$GO.Slim.Term, all.go.BP.slim$Location)
tabl1
  #                                  Florida Hawaii
  # cell adhesion                          8     38
  # cell cycle and proliferation          11     72
  # cell organization and biogenesis      44    153
  # cell-cell signaling                   18     18
  # death                                 14     12
  # developmental processes              174    695
  # DNA metabolism                         7     34
  # protein metabolism                    53    109
  # RNA metabolism                        52     75
  # signal transduction                   52     96
  # stress response                       46    101
  # transport                             63     66

rowSums(tabl1)
             #       cell adhesion     cell cycle and proliferation cell organization and biogenesis 
             #                  46                               83                              197 
             # cell-cell signaling                            death          developmental processes 
             #                  36                               26                              869 
             #      DNA metabolism               protein metabolism                   RNA metabolism 
             #                  41                              162                              127 
             # signal transduction                  stress response                        transport 
             #                 148                              147                              129 

colSums(tabl1)
# Florida  Hawaii 
#     542    1469
    
prop.table(table(all.go.BP.slim$GO.Slim.Term, all.go.BP.slim$Location)) * 100
  #                                     Florida     Hawaii
  # cell adhesion                     0.3978120  1.8896072
  # cell cycle and proliferation      0.5469915  3.5803083
  # cell organization and biogenesis  2.1879662  7.6081551
  # cell-cell signaling               0.8950771  0.8950771
  # death                             0.6961711  0.5967181
  # developmental processes           8.6524117 34.5599204
  # DNA metabolism                    0.3480855  1.6907011
  # protein metabolism                2.6355047  5.4201890
  # RNA metabolism                    2.5857782  3.7294878
  # signal transduction               2.5857782  4.7737444
  # stress response                   2.2874192  5.0223769
  # transport                         3.1327698  3.2819493

chisq.test(all.go.BP.slim$GO.Slim.Term, all.go.BP.slim$Location)
# 	Pearson's Chi-squared test
# 
# data:  all.go.BP.slim$GO.Slim.Term and all.go.BP.slim$Location
# X-squared = 107.86, df = 11, p-value < 2.2e-16


# By morphology 
tabl2 <- table(all.go.BP.slim$GO.Slim.Term, all.go.BP.slim$Morphology)
tabl2
  #                                  Branching Massive
  # cell adhesion                           40       6
  # cell cycle and proliferation            73      10
  # cell organization and biogenesis       139      58
  # cell-cell signaling                     30       6
  # death                                   21       5
  # developmental processes                735     134
  # DNA metabolism                          19      22
  # protein metabolism                     116      46
  # RNA metabolism                         105      22
  # signal transduction                    108      40
  # stress response                        126      21
  # transport                              107      22

rowSums(tabl2)
             #       cell adhesion     cell cycle and proliferation cell organization and biogenesis 
             #                  46                               83                              197 
             # cell-cell signaling                            death          developmental processes 
             #                  36                               26                              869 
             #      DNA metabolism               protein metabolism                   RNA metabolism 
             #                  41                              162                              127 
             # signal transduction                  stress response                        transport 
             #                 148                              147                              129 

colSums(tabl2)
# Branching   Massive 
#      1619       392

prop.table(table(all.go.BP.slim$GO.Slim.Term, all.go.BP.slim$Morphology)) * 100
  #                                   Branching    Massive
  # cell adhesion                     1.9890602  0.2983590
  # cell cycle and proliferation      3.6300348  0.4972650
  # cell organization and biogenesis  6.9119841  2.8841372
  # cell-cell signaling               1.4917951  0.2983590
  # death                             1.0442566  0.2486325
  # developmental processes          36.5489806  6.6633516
  # DNA metabolism                    0.9448036  1.0939831
  # protein metabolism                5.7682745  2.2874192
  # RNA metabolism                    5.2212829  1.0939831
  # signal transduction               5.3704625  1.9890602
  # stress response                   6.2655395  1.0442566
  # transport                         5.3207360  1.0939831

chisq.test(all.go.BP.slim$GO.Slim.Term, all.go.BP.slim$Morphology)
# Pearson's Chi-squared test
# 
# data:  all.go.BP.slim$GO.Slim.Term and all.go.BP.slim$Morphology
# X-squared = 73.386, df = 11, p-value = 2.762e-11
```




# Subset by GO slim term and plot for all species 
In the manuscript, only the BP terms will be presented. The CC and MF terms will be included in the supplementary materials

## BP
### Determine all categories to plot by
```{r}
unique(all.go.BP.slim$GO.Slim.Term)
#  [1] "transport"                        "RNA metabolism"                  
#  [3] "cell organization and biogenesis" "protein metabolism"              
#  [5] "DNA metabolism"                   "stress response"                 
#  [7] "developmental processes"          "cell cycle and proliferation"    
#  [9] "cell adhesion"                    "death"                           
# [11] "signal transduction"              "cell-cell signaling"  
```

Look at all_GOslim.BP plot to see which GOslim term has the most associated GO terms. Then, plot by that GOslim term. 

(1) "cell adhesion"
(2) "cell cycle and proliferation"
(3) "cell organization and biogenesis"
(4) "cell-cell signaling"
(5) "death"
(6) "developmental processes"
(7) "DNA metabolism"
#(8) "other biological processes"
#(9) "other metabolic processes"
(10) "protein metabolism"
(11) "RNA metabolism"
(12) "signal transduction" 
(13) "stress response"
(14) "transport 


### BP Plots 

(1) "cell adhesion"
```{r}
go.slim.CA.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="cell adhesion")

GO.CA.subset <- ggplot(go.slim.CA.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.CA.subset
ggsave("Output/Figs/CA.Subset_GOslim.BP_20220417.pdf", GO.CA.subset, width = 40, height = 40, units = c("in"))
```


(2) "cell cycle and proliferation"
```{r}
go.slim.CCP.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="cell cycle and proliferation")

GO.CCP.subset <- ggplot(go.slim.CCP.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.CCP.subset
ggsave("Output/Figs/CCP.Subset_GOslim.BP_20220417.pdf", GO.CCP.subset, width = 40, height = 40, units = c("in"))
```


(3) "cell organization and biogenesis"
```{r}
go.slim.COB.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="cell organization and biogenesis")

GO.COB.subset <- ggplot(go.slim.COB.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.COB.subset
ggsave("Output/Figs/COB.Subset_GOslim.BP_20220417.pdf", GO.COB.subset, width = 40, height = 40, units = c("in"))
```


(4) "cell-cell signaling"
```{r}
go.slim.CCS.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="cell-cell signaling")

GO.CCS.subset <- ggplot(go.slim.CCS.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.CCS.subset
ggsave("Output/Figs/CCS.Subset_GOslim.BP_20220417.pdf", GO.CCS.subset, width = 40, height = 40, units = c("in"))
```


(5) "death"
```{r}
go.slim.Death.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="death")

GO.death.subset <- ggplot(go.slim.Death.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.death.subset
ggsave("Output/Figs/Death.Subset_GOslim.BP_20220417.pdf", GO.death.subset, width = 40, height = 40, units = c("in"))
```

(6) "developmental processes"
```{r}
go.slim.DP.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="developmental processes")

GO.DP.subset <- ggplot(go.slim.DP.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.DP.subset
ggsave("Output/Figs/DP.Subset_GOslim.BP_20220417.pdf", GO.DP.subset, width = 40, height = 40, units = c("in"))
```


(7) "DNA metabolism"
```{r}
go.slim.DNAM.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="DNA metabolism")

GO.DNAM.subset <- ggplot(go.slim.DNAM.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.DNAM.subset
ggsave("Output/Figs/DNAM.Subset_GOslim.BP_20220417.pdf", GO.DNAM.subset, width = 40, height = 40, units = c("in"))
```

(8) "other biological processes"
```{r}
go.slim.OBP.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="other biological processes")

GO.OBP.subset <- ggplot(go.slim.OBP.subset, aes(x = Species, y = term)) +
  geom_tile(aes(fill =over_represented_pvalue)) +
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.OBP.subset
ggsave("Output/Figs/OBP.Subset_GOslim.BP_20220417.pdf", GO.OBP.subset, width = 40, height = 40, units = c("in"))
```

(9) "other metabolic processes"
```{r}
go.slim.OMP.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="other metabolic processes")

GO.OMP.subset <- ggplot(go.slim.OMP.subset, aes(x = Species, y = term)) +
  geom_tile(aes(fill =over_represented_pvalue)) +
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.OMP.subset
ggsave("Output/Figs/OMP.Subset_GOslim.BP_20220417.pdf", GO.OMP.subset, width = 40, height = 40, units = c("in"))
```

(10) "protein metabolism"
```{r}
go.slim.PM.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="protein metabolism")

GO.PM.subset <- ggplot(go.slim.PM.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.PM.subset
ggsave("Output/Figs/PM.Subset_GOslim.BP_20220417.pdf", GO.PM.subset, width = 40, height = 40, units = c("in"))
```

(11) "RNA metabolism"
```{r}
go.slim.RNAM.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="RNA metabolism")

GO.RNAM.subset <- ggplot(go.slim.RNAM.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.RNAM.subset
ggsave("Output/Figs/RNAM.Subset_GOslim.BP_20220417.pdf", GO.RNAM.subset, width = 40, height = 40, units = c("in"))
```

(12) "signal transduction"
```{r}
go.slim.ST.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="signal transduction")

GO.ST.subset <- ggplot(go.slim.ST.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.ST.subset
ggsave("Output/Figs/ST.Subset_GOslim.BP_20220417.pdf", GO.ST.subset, width = 40, height = 40, units = c("in"))
```

(13) "stress response"
```{r}
go.slim.SR.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="stress response")

GO.SR.subset <- ggplot(go.slim.SR.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.SR.subset
ggsave("Output/Figs/SR.Subset_GOslim.BP_20220417.pdf", GO.SR.subset, width = 40, height = 40, units = c("in"))
```

(14) "transport"
```{r}
go.slim.T.subset <- all.go.BP.slim %>% filter(GO.Slim.Term=="transport")

GO.T.subset <- ggplot(go.slim.T.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.T.subset
ggsave("Output/Figs/Transport.Subset_GOslim.BP_20220417.pdf", GO.T.subset, width = 40, height = 40, units = c("in"))
```







































### CC and MF will be included in supplementary materials

Make bar charts for go slim term counts for species, locations, and morphologies - CC only
```{r}
# read in data
all.go.CC.slim <- read.csv("Output/GOSeq/all.go.CC.slim_20220417.csv", header = T)

# Check species names
unique(all.go.CC.slim$Species)
# "A.cervicornis" "M.cavernosa"   "O.faveolata"   "M.capitata"   "P.acuta"       "P.lobata"  

# for this plot, remove NAs
all.go.CC.slim <- subset(all.go.CC.slim, !GO.Slim.Term == "NA")

# plot by species 
## plotting unique GO terms only - if I plot with all.go.BP.slim, I get duplicate GO slim terms bc its duplicating based on gene id/treatment?
test <- select(all.go.CC.slim, c("GO.IDs", "term", "Species", "GO.Slim.Term"))
test <- unique(test)
test <- na.omit(test)

# count GOslim by species
count_by_group <- test %>%
  dplyr::count(Species, GO.Slim.Term)
count_by_group

# plot
count <- ggplot(count_by_group, aes(fill = Species, y = n, x = GO.Slim.Term)) +
  geom_bar(position = "dodge", 
           stat = "identity", 
           width = 0.9) +
  # geom_text(aes(label = n), 
  #           position = position_dodge(0.9), 
  #           size = 10, 
  #           face = "bold") +
  labs(title="Counts of GO Slim Categories", x ="", y = "Counts") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 65, 
                                   #vjust = 0.5, 
                                   hjust= 1, 
                                   size=60)) + 
  theme(axis.text.y = element_text(size = 60)) +
  theme(axis.title.y = element_text(size = 40)) +
  theme(plot.title = element_text(size = 100, hjust = 0.5)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 20)) + 
  theme(legend.title = element_text(size = 60), 
        legend.key.size = unit(2, "cm"),
        legend.text = element_text(size=60), 
        legend.position = c(0.85, 0.85), 
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.background = element_rect(fill = "white", color = "black")) + 
  scale_fill_manual(values = c("dodgerblue", "goldenrod1", "darkorange1", "seagreen3", "orchid3", "grey"))
count
ggsave("Output/Figs/SpeciesCounts_GOslim.CC_20220417.pdf", count, width = 40, height = 30, units = c("in"))
ggsave("Output/Figs/SpeciesCounts_GOslim.CC_20220417.png", count, width = 40, height = 30, units = c("in"))

# plot by location/sediment type
all.go.CC.slim <- all.go.CC.slim %>% mutate(Location = 
                                              case_when(Species == "A.cervicornis" ~ "Florida", 
                                                        Species == "M.cavernosa" ~ "Florida",
                                                        Species == "O.faveolata" ~ "Florida",
                                                        Species == "M.capitata" ~ "Hawaii",
                                                        Species == "P.acuta" ~ "Hawaii",
                                                        Species == "P.lobata" ~ "Hawaii"))

# count GOslim by location
count_by_location <- all.go.CC.slim %>%
  dplyr::count(Location, GO.Slim.Term)
count_by_location

# plot
count_location_plot <- ggplot(count_by_location, aes(fill = Location, y = n, x = GO.Slim.Term)) +
  geom_bar(position = "dodge", 
           stat = "identity", 
           colour="black",
           width = 0.9,
           size = 2) +
  # geom_text(aes(label = n), 
  #           position = position_dodge(0.9), 
  #           size = 10, 
  #           face = "bold") +
  ylab("GO Term Counts\n") + 
  #ggtitle(label = "Counts of GO Slim Categories by Location") +
  #coord_flip() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 65,
                                   #vjust = 0.5, 
                                   hjust= 1, 
                                   size=80, 
                                   colour = "black"), 
        axis.text.y = element_text(size = 60, colour = "black"),
        axis.title.y = element_text(size = 80, face = "bold"),
        axis.line = element_line(colour = 'black', size = 2),
        plot.title = element_text(size = 100, hjust = 0.5),
        plot.margin = margin(3,3,3,3, "cm")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, 120)) + 
  theme(legend.title = element_text(size = 80), 
        legend.key.size = unit(2, "cm"),
        legend.text = element_text(size=80), 
        legend.position = c(0.85, 0.85), 
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.background = element_rect(fill = "white", color = "black"),
        legend.box.background = element_rect(color="black", size=2)) +
        scale_fill_manual(values = c("chartreuse3", "chocolate2"))
count_location_plot
ggsave("Output/Figs/LocationsCounts_GOslim.CC_20220417.pdf", count_location_plot, width = 49, height = 40, units = c("in"))
ggsave("Output/Figs/LocationsCounts_GOslim.CC_20220417.png", count_location_plot, width = 49, height = 40, units = c("in"))

# plot by morphology type
all.go.CC.slim <- all.go.CC.slim %>% mutate(Morphology = 
                                              case_when(Species == "A.cervicornis" ~ "Branching", 
                                                        Species == "M.cavernosa" ~ "Massive",
                                                        Species == "O.faveolata" ~ "Massive",
                                                        Species == "M.capitata" ~ "Branching",
                                                        Species == "P.acuta" ~ "Branching",
                                                        Species == "P.lobata" ~ "Massive"))

# count GOslim by morphology
count_by_morph <- all.go.CC.slim %>%
  dplyr::count(Morphology, GO.Slim.Term)
count_by_morph

# plot
count_morph_plot <- ggplot(count_by_morph, aes(fill = Morphology, y = n, x = GO.Slim.Term)) +
    geom_bar(position = "dodge", 
           stat = "identity", 
           colour="black",
           width = 0.9,
           size = 2) +
  # geom_text(aes(label = n), 
  #           position = position_dodge(0.9), 
  #           size = 10, 
  #           face = "bold") +
  ylab("GO Term Counts\n") + 
  #ggtitle(label = "Counts of GO Slim Categories by Morphology") +
  #coord_flip() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 65,
                                   #vjust = 0.5, 
                                   hjust= 1, 
                                   size=80, 
                                   colour = "black"), 
        axis.text.y = element_text(size = 60, colour = "black"),
        axis.title.y = element_text(size = 80, face = "bold"),
        axis.line = element_line(colour = 'black', size = 2),
        plot.title = element_text(size = 100, hjust = 0.5),
        plot.margin = margin(3,3,3,3, "cm")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, 125)) + 
  theme(legend.title = element_text(size = 80), 
        legend.key.size = unit(2, "cm"),
        legend.text = element_text(size=80), 
        legend.position = c(0.85, 0.85), 
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.background = element_rect(fill = "white", color = "black"),
        legend.box.background = element_rect(color="black", size=2)) +
        scale_fill_manual(values = c("paleturquoise3", "rosybrown2"))
count_morph_plot
ggsave("Output/Figs/MorphologyCounts_GOslim.CC_20220417.pdf", count_morph_plot, width = 49, height = 40, units = c("in"))
ggsave("Output/Figs/MorphologyCounts_GOslim.CC_20220417.png", count_morph_plot, width = 49, height = 40, units = c("in"))
```

Make bar charts for go slim term counts for species, locations, and morphologies - MF only
```{r}
# read in data
all.go.MF.slim <- read.csv("Output/GOSeq/all.go.MF.slim_20220417.csv", header = T)

# Check species names
unique(all.go.MF.slim$Species)
# "A.cervicornis" "M.cavernosa"   "O.faveolata"   "M.capitata"   "P.acuta"       "P.lobata"  

# for this plot, remove NAs
all.go.MF.slim <- subset(all.go.MF.slim, !GO.Slim.Term == "NA")

# plot by species 
## plotting unique GO terms only - if I plot with all.go.BP.slim, I get duplicate GO slim terms bc its duplicating based on gene id/treatment?
test <- select(all.go.MF.slim, c("GO.IDs", "term", "Species", "GO.Slim.Term"))
test <- unique(test)
test <- na.omit(test)

# count GOslim by species
count_by_group <- test %>%
  dplyr::count(Species, GO.Slim.Term)
count_by_group

# plot
count <- ggplot(count_by_group, aes(fill = Species, y = n, x = GO.Slim.Term)) +
  geom_bar(position = "dodge", 
           stat = "identity", 
           width = 0.9) +
  # geom_text(aes(label = n), 
  #           position = position_dodge(0.9), 
  #           size = 10, 
  #           face = "bold") +
  labs(title="Counts of GO Slim Categories", x ="", y = "Counts") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 65, 
                                   #vjust = 0.5, 
                                   hjust= 1, 
                                   size=60)) + 
  theme(axis.text.y = element_text(size = 60)) +
  theme(axis.title.y = element_text(size = 40)) +
  theme(plot.title = element_text(size = 100, hjust = 0.5)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) + 
  theme(legend.title = element_text(size = 60), 
        legend.key.size = unit(2, "cm"),
        legend.text = element_text(size=60), 
        legend.position = c(0.85, 0.85), 
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.background = element_rect(fill = "white", color = "black")) + 
  scale_fill_manual(values = c("dodgerblue", "goldenrod1", "darkorange1", "seagreen3", "orchid3", "grey"))
count
ggsave("Output/Figs/SpeciesCounts_GOslim.MF_20220417.pdf", count, width = 40, height = 30, units = c("in"))
ggsave("Output/Figs/SpeciesCounts_GOslim.MF_20220417.png", count, width = 40, height = 30, units = c("in"))

# plot by location/sediment type
all.go.MF.slim <- all.go.MF.slim %>% mutate(Location = 
                                              case_when(Species == "A.cervicornis" ~ "Florida", 
                                                        Species == "M.cavernosa" ~ "Florida",
                                                        Species == "O.faveolata" ~ "Florida",
                                                        Species == "M.capitata" ~ "Hawaii",
                                                        Species == "P.acuta" ~ "Hawaii",
                                                        Species == "P.lobata" ~ "Hawaii"))

# count GOslim by location
count_by_location <- all.go.MF.slim %>%
  dplyr::count(Location, GO.Slim.Term)
count_by_location

# plot
count_location_plot <- ggplot(count_by_location, aes(fill = Location, y = n, x = GO.Slim.Term)) +
  geom_bar(position = "dodge", 
           stat = "identity", 
           colour="black",
           width = 0.9,
           size = 2) +
  # geom_text(aes(label = n), 
  #           position = position_dodge(0.9), 
  #           size = 10, 
  #           face = "bold") +
  ylab("GO Term Counts\n") + 
  #ggtitle(label = "Counts of GO Slim Categories by Location") +
  #coord_flip() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 65,
                                   #vjust = 0.5, 
                                   hjust= 1, 
                                   size=80, 
                                   colour = "black"), 
        axis.text.y = element_text(size = 60, colour = "black"),
        axis.title.y = element_text(size = 80, face = "bold"),
        axis.line = element_line(colour = 'black', size = 2),
        plot.title = element_text(size = 100, hjust = 0.5),
        plot.margin = margin(3,3,3,3, "cm")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, 400)) + 
  theme(legend.title = element_text(size = 80), 
        legend.key.size = unit(2, "cm"),
        legend.text = element_text(size=80), 
        legend.position = c(0.85, 0.85), 
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.background = element_rect(fill = "white", color = "black"),
        legend.box.background = element_rect(color="black", size=2)) +
        scale_fill_manual(values = c("chartreuse3", "chocolate2"))
count_location_plot
ggsave("Output/Figs/LocationsCounts_GOslim.MF_20220417.pdf", count_location_plot, width = 49, height = 40, units = c("in"))
ggsave("Output/Figs/LocationsCounts_GOslim.MF_20220417.png", count_location_plot, width = 49, height = 40, units = c("in"))

# plot by morphology type
all.go.MF.slim <- all.go.MF.slim %>% mutate(Morphology = 
                                              case_when(Species == "A.cervicornis" ~ "Branching", 
                                                        Species == "M.cavernosa" ~ "Massive",
                                                        Species == "O.faveolata" ~ "Massive",
                                                        Species == "M.capitata" ~ "Branching",
                                                        Species == "P.acuta" ~ "Branching",
                                                        Species == "P.lobata" ~ "Massive"))

# count GOslim by morphology
count_by_morph <- all.go.MF.slim %>%
  dplyr::count(Morphology, GO.Slim.Term)
count_by_morph

# plot
count_morph_plot <- ggplot(count_by_morph, aes(fill = Morphology, y = n, x = GO.Slim.Term)) +
    geom_bar(position = "dodge", 
           stat = "identity", 
           colour="black",
           width = 0.9,
           size = 2) +
  # geom_text(aes(label = n), 
  #           position = position_dodge(0.9), 
  #           size = 10, 
  #           face = "bold") +
  ylab("GO Term Counts\n") + 
  #ggtitle(label = "Counts of GO Slim Categories by Morphology") +
  #coord_flip() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 65,
                                   #vjust = 0.5, 
                                   hjust= 1, 
                                   size=80, 
                                   colour = "black"), 
        axis.text.y = element_text(size = 60, colour = "black"),
        axis.title.y = element_text(size = 80, face = "bold"),
        axis.line = element_line(colour = 'black', size = 2),
        plot.title = element_text(size = 100, hjust = 0.5),
        plot.margin = margin(3,3,3,3, "cm")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, 400)) + 
  theme(legend.title = element_text(size = 80), 
        legend.key.size = unit(2, "cm"),
        legend.text = element_text(size=80), 
        legend.position = c(0.85, 0.85), 
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.background = element_rect(fill = "white", color = "black"),
        legend.box.background = element_rect(color="black", size=2)) +
        scale_fill_manual(values = c("paleturquoise3", "rosybrown2"))
count_morph_plot
ggsave("Output/Figs/MorphologyCounts_GOslim.MF_20220417.pdf", count_morph_plot, width = 49, height = 40, units = c("in"))
ggsave("Output/Figs/MorphologyCounts_GOslim.MF_20220417.png", count_morph_plot, width = 49, height = 40, units = c("in"))
```







## CC
### Determine all categories to plot by
```{r}
unique(all.go.CC.slim$GO.Slim.Term)
# [1] "other cellular component"     "nucleus"                      "other membranes"             
#  [4] "other cytoplasmic organelle"  "cytoskeleton"                 "ER/Golgi"                    
#  [7] "plasma membrane"              "mitochondrion"                "non-structural extracellular"
# [10] "cytosol"                      "translational apparatus"                                       
```

Look at all_GOslim.CC plot to see which GOslim term has the most associated GO terms. Then, plot by that GOslim term. Going to subset and plot by GOslim terms that appear in all_GOslim.CC_20220125.pdf: 

(1) cytoskeleton
(2) ER/Golgi
(3) plasma membrane
(4) mitochondrion
(5) non-structural extracellular
(6) nucleus
(7) other cellular component
(8) other cytoplasmic organelle
(9) other membranes
(10) cytosol
(11) translational apparatus


(1) "cytoskeleton"
```{r}
go.slim.Cytoskeleton.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="cytoskeleton")

GO.Cytoskeleton.subset <- ggplot(go.slim.Cytoskeleton.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.Cytoskeleton.subset
ggsave("Output/Figs/Cytoskeleton.Subset_GOslim.CC_20220419.pdf", GO.Cytoskeleton.subset, width = 40, height = 40, units = c("in"))
```

(2) "ER/Golgi"
```{r}
go.slim.EG.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="ER/Golgi")

GO.EG.subset <- ggplot(go.slim.EG.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.EG.subset
ggsave("Output/Figs/EG.Subset_GOslim.CC_20220419.pdf", GO.EG.subset, width = 40, height = 40, units = c("in"))
```

(3) "plasma membrane"
```{r}
go.slim.PMem.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="plasma membrane")

GO.PMem.subset <- ggplot(go.slim.PMem.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.PMem.subset
ggsave("Output/Figs/PMem.Subset_GOslim.CC_20220419.pdf", GO.PMem.subset, width = 40, height = 40, units = c("in"))
```

(4) 'mitochondrion'
```{r}
go.slim.Mito.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="mitochondrion")

GO.Mito.subset <- ggplot(go.slim.Mito.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.Mito.subset
ggsave("Output/Figs/Mito.Subset_GOslim.CC_20220419.pdf", GO.Mito.subset, width = 40, height = 40, units = c("in"))
```

(5) 'non-structural extracellular'
```{r}
go.slim.NSE.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="non-structural extracellular")

GO.NSE.subset <- ggplot(go.slim.NSE.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.NSE.subset
ggsave("Output/Figs/NSE.Subset_GOslim.CC_20220419.pdf", GO.NSE.subset, width = 40, height = 40, units = c("in"))
```

(6) 'nucleus'
```{r}
go.slim.Nucleus.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="nucleus")

GO.Nucleus.subset <- ggplot(go.slim.Nucleus.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.Nucleus.subset
ggsave("Output/Figs/Nucleus.Subset_GOslim.CC_20220419.pdf", GO.Nucleus.subset, width = 40, height = 40, units = c("in"))
```

(7) 'other cellular component'
```{r}
go.slim.OCC.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="other cellular component")

GO.OCC.subset <- ggplot(go.slim.OCC.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.OCC.subset
ggsave("Output/Figs/OCC.Subset_GOslim.CC_20220419.pdf", GO.OCC.subset, width = 40, height = 40, units = c("in"))
```

(8) 'other cytoplasmic organelle'
```{r}
go.slim.OCO.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="other cytoplasmic organelle")

GO.OCO.subset <- ggplot(go.slim.OCO.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.OCO.subset
ggsave("Output/Figs/OCO.Subset_GOslim.CC_20220419.pdf", GO.OCO.subset, width = 40, height = 40, units = c("in"))
```

(9) 'other membranes'
```{r}
go.slim.OM.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="other membranes")

GO.OM.subset <- ggplot(go.slim.OM.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.OM.subset
ggsave("Output/Figs/OM.Subset_GOslim.CC_20220419.pdf", GO.OM.subset, width = 40, height = 40, units = c("in"))
```

(10) 'cytosol'
```{r}
go.slim.Cytosol.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="cytosol")

GO.Cytosol.subset <- ggplot(go.slim.Cytosol.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.Cytosol.subset
ggsave("Output/Figs/Cytosol.Subset_GOslim.CC_20220419.pdf", GO.Cytosol.subset, width = 40, height = 40, units = c("in"))
```

(11) 'translational apparatus'
```{r}
go.slim.TA.subset <- all.go.CC.slim %>% filter(GO.Slim.Term=="translational apparatus")

GO.TA.subset <- ggplot(go.slim.TA.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.TA.subset
ggsave("Output/Figs/TA.Subset_GOslim.CC_20220419.pdf", GO.TA.subset, width = 40, height = 40, units = c("in"))
```



## MF
### Determine all categories to plot by
```{r}
unique(all.go.MF.slim$GO.Slim.Term)
# [1] "signal transduction activity"      "other molecular function"          "nucleic acid binding activity"    
# [4] "kinase activity"                   "transporter activity"              "enzyme regulator activity"        
# [7] "transcription regulatory activity" "cytoskeletal activity"                             
```

Look at all_GOslim.MF plot to see which GOslim term has the most associated GO terms. Then, plot by that GOslim term. Going to subset and plot by GOslim terms that appear in all_GOslim.MF_20220125.pdf: 


(1) cytoskeletal activity
(2) enzyme regulator activity
(3) kinase activity
(4) nucleic acid binding activity
(5) other molecular function
(6) signal transduction activity
(7) transcription regulatory activity
(8) transporter activity


(1) 'cytoskeletal activity'
```{r}
go.slim.CytoA.subset <- all.go.MF.slim %>% filter(GO.Slim.Term=="cytoskeletal activity")

GO.CtyoA.subset <- ggplot(go.slim.CytoA.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.CtyoA.subset
ggsave("Output/Figs/CytoA.Subset_GOslim.MF_20220419.pdf", GO.CtyoA.subset, width = 40, height = 40, units = c("in"))
```

(2) 'enzyme regulator activity'
```{r}
go.slim.ERA.subset <- all.go.MF.slim %>% filter(GO.Slim.Term=="enzyme regulator activity")

GO.ERA.subset <- ggplot(go.slim.ERA.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.ERA.subset
ggsave("Output/Figs/ERA.Subset_GOslim.MF_20220419.pdf", GO.ERA.subset, width = 40, height = 40, units = c("in"))
```

(3) 'kinase activity'
```{r}
go.slim.KA.subset <- all.go.MF.slim %>% filter(GO.Slim.Term=="kinase activity")

GO.KA.subset <- ggplot(go.slim.KA.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.KA.subset
ggsave("Output/Figs/KA.Subset_GOslim.MF_20220419.pdf", GO.KA.subset, width = 40, height = 40, units = c("in"))
```

(4) 'nucleic acid binding activity'
```{r}
go.slim.NABA.subset <- all.go.MF.slim %>% filter(GO.Slim.Term=="nucleic acid binding activity")

GO.NABA.subset <- ggplot(go.slim.NABA.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.NABA.subset
ggsave("Output/Figs/NABA.Subset_GOslim.MF_20220419.pdf", GO.NABA.subset, width = 40, height = 40, units = c("in"))
```

(5) 'other molecular function'
```{r}
go.slim.OMF.subset <- all.go.MF.slim %>% filter(GO.Slim.Term=="other molecular function")

GO.OMF.subset <- ggplot(go.slim.OMF.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.OMF.subset
ggsave("Output/Figs/OMG.Subset_GOslim.MF_20220419.pdf", GO.OMF.subset, width = 40, height = 40, units = c("in"))
```

(6) 'signal transduction activity'
```{r}
go.slim.STA.subset <- all.go.MF.slim %>% filter(GO.Slim.Term=="signal transduction activity")

GO.STA.subset <- ggplot(go.slim.STA.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.STA.subset
ggsave("Output/Figs/STA.Subset_GOslim.MF_20220419.pdf", GO.STA.subset, width = 40, height = 40, units = c("in"))
```

(7) 'transcription regulatory activity'
```{r}
go.slim.TRA.subset <- all.go.MF.slim %>% filter(GO.Slim.Term=="transcription regulatory activity")

GO.TRA.subset <- ggplot(go.slim.TRA.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.TRA.subset
ggsave("Output/Figs/TRA.Subset_GOslim.MF_20220419.pdf", GO.TRA.subset, width = 40, height = 40, units = c("in"))
```

(8) 'transporter activity'
```{r}
go.slim.TA.subset <- all.go.MF.slim %>% filter(GO.Slim.Term=="transporter activity")

GO.TA.subset <- ggplot(go.slim.TA.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.TA.subset
ggsave("Output/Figs/TA.Subset_GOslim.MF_20220419.pdf", GO.TA.subset, width = 40, height = 40, units = c("in"))
```
