---
title: "GOslim"
author: "jillashey"
date: "10/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages 
library(readr)
library(arsenal)
library(tidyverse)
```

# GO slim plots for HI corals 

## Pdam 
```{r}
# Read in pdam info
pdam.go <- read_csv("Output/SuppTables/Pdamicornis_DEG_SuppTable.csv", locale = locale(encoding = "Latin1"))
pdam.go <- select(pdam.go, c("category", "term", "ontology", "over_represented_pvalue", "Treatment_Compare"))
colnames(pdam.go)[1] <-"GO.IDs" # rename column with GO terms to GO.IDs
length(unique(pdam.go$term)) # 50 GO terms

# Read in GOslim info
go.slim <- read_csv("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/GOSeq/GO-GOslim.csv")
colnames(go.slim) <- c("GO.IDs", "GO.Term", "GO.Slim.Term", "Cat") #rename columns
Gene.GO.IDs.slims.pdam <- merge(pdam.go, go.slim, by="GO.IDs", all = TRUE) # merge pdam info and GOslim
Gene.GO.IDs.slims.pdam <- na.omit(Gene.GO.IDs.slims.pdam)

# Plot pdam goslim
GO.pdam <- ggplot(Gene.GO.IDs.slims.pdam, aes(x = ontology, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.pdam
ggsave("Output/Figs/pdam/pdam_GOslim_20211011.pdf", GO.pdam, width = 28, height = 28)
```

## Plob 
```{r}
plob.go <- read_csv("Output/SuppTables/Plobata_DEG_SuppTable.csv", locale = locale(encoding = "Latin1"))
plob.go <- select(plob.go, c("category", "term", "ontology", "over_represented_pvalue", "Treatment_Compare"))
colnames(plob.go)[1] <-"GO.IDs"
length(unique(plob.go$term)) # 20 GO terms 

go.slim <- read_csv("Output/GOSeq/GO-GOslim.csv")
colnames(go.slim) <- c("GO.IDs", "GO.Term", "GO.Slim.Term", "Cat") #rename columns
Gene.GO.IDs.slims.plob <- merge(plob.go, go.slim, by="GO.IDs", all = TRUE)
Gene.GO.IDs.slims.plob <- na.omit(Gene.GO.IDs.slims.plob)

GO.plob <- ggplot(Gene.GO.IDs.slims.plob, aes(x = ontology, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.plob
ggsave("Output/Figs/plob/plob_GOslim_20211011.pdf", GO.plob, width = 28, height = 28, units = c("in"))
```


# GO slim plots for FL corals 

## Acerv
```{r}
acerv.go <- read_csv("Output/SuppTables/Acervicornis_DEG_SuppTable.csv", locale = locale(encoding = "Latin1"))
acerv.go <- select(acerv.go, c("category", "term", "ontology", "over_represented_pvalue", "Treatment_Compare"))
colnames(acerv.go)[1] <-"GO.IDs"

# Renaming specific term in Acerv because it is very long and makes the plots look weird
acerv.go$term <- gsub("oxidoreductase activity, acting on paired donors, with incorporation or reduction of molecular oxygen, reduced flavin or flavoprotein as one donor, and incorporation of one atom of oxygen", "oxidoreductase activity", acerv.go$term)

go.slim <- read_csv("Output/GOSeq/GO-GOslim.csv")
colnames(go.slim) <- c("GO.IDs", "GO.Term", "GO.Slim.Term", "Cat") #rename columns
Gene.GO.IDs.slims.acerv <- merge(acerv.go, go.slim, by="GO.IDs", all = TRUE)
Gene.GO.IDs.slims.acerv <- na.omit(Gene.GO.IDs.slims.acerv)

GO.acerv <- ggplot(Gene.GO.IDs.slims.acerv, aes(x = ontology, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.acerv
ggsave("Output/Figs/acerv/acerv_GOslim_20211011.pdf", GO.acerv, width = 28, height = 28, units = c("in"))
```

## Mcav 
```{r}
mcav.go <- read_csv("Output/SuppTables/Mcavernosa_DEG_SuppTable.csv", locale = locale(encoding = "Latin1"))
mcav.go <- select(mcav.go, c("category", "term", "ontology", "over_represented_pvalue", "Treatment_Compare"))
colnames(mcav.go)[1] <-"GO.IDs"

go.slim <- read_csv("Output/GOSeq/GO-GOslim.csv")
colnames(go.slim) <- c("GO.IDs", "GO.Term", "GO.Slim.Term", "Cat") #rename columns
Gene.GO.IDs.slims.mcav <- merge(mcav.go, go.slim, by="GO.IDs", all = TRUE)
Gene.GO.IDs.slims.mcav <- na.omit(Gene.GO.IDs.slims.mcav)

GO.mcav <- ggplot(Gene.GO.IDs.slims.mcav, aes(x = ontology, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.mcav
ggsave("Output/Figs/mcav/mcav_GOslim_20211011.pdf", GO.mcav, width = 28, height = 28, units = c("in"))

```


# All species 

## Plot all species on one GO slim plot 
```{r}
# Add species name and site to each df
Gene.GO.IDs.slims.pdam$Species <- "P.damicornis"
Gene.GO.IDs.slims.pdam$Site <- "Hawaii"
Gene.GO.IDs.slims.plob$Species <- "P.lobata"
Gene.GO.IDs.slims.plob$Site <- "Hawaii"
Gene.GO.IDs.slims.acerv$Species <- "A.cervicornis"
Gene.GO.IDs.slims.acerv$Site <- "Florida"
Gene.GO.IDs.slims.mcav$Species <- "M.cavernosa"
Gene.GO.IDs.slims.mcav$Site <- "Florida"

# Bind all species df together for GO slim plot 
all.go.slim <- rbind(Gene.GO.IDs.slims.acerv, Gene.GO.IDs.slims.mcav, Gene.GO.IDs.slims.pdam, Gene.GO.IDs.slims.plob)

GO.all <- ggplot(all.go.slim, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.all
ggsave("Output/Figs/all_GOslim_20211011.pdf", GO.all, width = 28, height = 28, units = c("in"))
#ggsave("Output/Figs/all_GOslim_20210509.jpeg", GO.all, width = 28, height = 28, units = c("in"))
```

# Subset by ontology (BP, MF) and plot for all species 
```{r}
# Subset and plot by MF
go.slim.MF <- all.go.slim %>% filter(ontology=="MF")

GO.subset.MF <- ggplot(go.slim.MF, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.subset.MF
ggsave("Output/Figs/MF_GOslim_20211011.pdf", GO.subset.MF, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/MF_GOslim_20210705.jpeg", GO.subset.MF, width = 28, height = 28, units = c("in"))

# Subset and plot by BP
go.slim.BP <- all.go.slim %>% filter(ontology=="BP")

GO.subset.BP <- ggplot(go.slim.BP, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.subset.BP
ggsave("Output/Figs/BP_GOslim_20211011.pdf", GO.subset.BP, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/BP_GOslim_20210705.jpeg", GO.subset.BP, width = 28, height = 28, units = c("in"))
```

# Subset by GO slim term and plot for all species 
```{r}
# Subset and plot only 'other molecular function' (OMF)
go.slim.OMF.subset <- all.go.slim %>% filter(GO.Slim.Term=="other molecular function")

GO.OMF.subset <- ggplot(go.slim.OMF.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.OMF.subset
ggsave("Output/Figs/OMF.Subset_GOslim_20211011.pdf", GO.OMF.subset, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/OMF.Subset_GOslim_20211011.jpeg", GO.OMF.subset, width = 28, height = 28, units = c("in"))


# Subset and plot only 'other metabolic processes' (OMP)
go.slim.OMP.subset <- all.go.slim %>% filter(GO.Slim.Term=="other metabolic processes")

GO.OMP.subset <- ggplot(go.slim.OMP.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.OMP.subset
ggsave("Output/Figs/OMP.Subset_GOslim_20210509.pdf", GO.OMP.subset, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/OMP.Subset_GOslim_20210509.pdf", GO.OMP.subset, width = 28, height = 28, units = c("in"))
```

## Subset and plot by site 
```{r}
## FL
go.FL.subset <- all.go.slim %>% filter(Site=="Florida")

GO.FL_subset <- ggplot(go.FL.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.FL_subset
ggsave("Output/Figs/FL_GOslim_20211011.pdf", GO.FL_subset, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/FL_GOslim_20210509.jpeg", GO.FL_subset, width = 28, height = 28, units = c("in"))

## HI
go.HI.subset <- all.go.slim %>% filter(Site=="Hawaii")

GO.HI_subset <- ggplot(go.HI.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.HI_subset
ggsave("Output/Figs/HI_GOslim_20211011.pdf", GO.HI_subset, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/HI_GOslim_20210509.jpeg", GO.HI_subset, width = 28, height = 28, units = c("in"))
```

# Subset by ontology (BP, MF) and plot by site 
```{r}
## FL
# Subset and plot by MF
go.slim.FL.MF <- go.FL.subset %>% filter(ontology=="MF")

GO.subset.FL.MF <- ggplot(go.slim.FL.MF, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.subset.FL.MF
ggsave("Output/Figs/FL_MF_GOslim_20211011.pdf", GO.subset.FL.MF, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/MF_GOslim_20210705.jpeg", GO.subset.FL.MF, width = 28, height = 28, units = c("in"))

# Subset and plot by BP
go.slim.FL.BP <- go.FL.subset %>% filter(ontology=="BP")

GO.subset.FL.BP <- ggplot(go.slim.FL.BP, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.subset.FL.BP
ggsave("Output/Figs/FL_BP_GOslim_20211011.pdf", GO.subset.FL.BP, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/BP_GOslim_20210705.jpeg", GO.subset.FL.BP, width = 28, height = 28, units = c("in"))



## HI
# Subset and plot by MF
go.slim.HI.MF <- go.HI.subset %>% filter(ontology=="MF")

GO.subset.HI.MF <- ggplot(go.slim.HI.MF, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.subset.HI.MF
ggsave("Output/Figs/HI_MF_GOslim_20211011.pdf", GO.subset.HI.MF, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/MF_GOslim_20210705.jpeg", GO.subset.HI.MF, width = 28, height = 28, units = c("in"))

# Subset and plot by BP
go.slim.HI.BP <- go.HI.subset %>% filter(ontology=="BP")

GO.subset.HI.BP <- ggplot(go.slim.HI.BP, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.subset.HI.BP
ggsave("Output/Figs/HI_BP_GOslim_20211011.pdf", GO.subset.HI.BP, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/BP_GOslim_20210705.jpeg", GO.subset.HI.BP, width = 28, height = 28, units = c("in"))
```

# Subset by GO slim term and plot by site 
```{r}
## FL
# Subset and plot only 'other molecular function' (OMF)
go.slim.FL.OMF.subset <- go.FL.subset %>% filter(GO.Slim.Term=="other molecular function")

GO.FL.OMF.subset <- ggplot(go.slim.FL.OMF.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.FL.OMF.subset
ggsave("Output/Figs/FL_OMF.Subset_GOslim_20211011.pdf", GO.FL.OMF.subset, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/OMF.Subset_GOslim_20211011.jpeg", GO.FL.OMF.subset, width = 28, height = 28, units = c("in"))

# Subset and plot only 'other metabolic processes' (OMP)
go.slim.FL.OMP.subset <- go.FL.subset %>% filter(GO.Slim.Term=="other metabolic processes")

GO.FL.OMP.subset <- ggplot(go.slim.FL.OMP.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.FL.OMP.subset
ggsave("Output/Figs/FL_OMP.Subset_GOslim_20211011.pdf", GO.FL.OMP.subset, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/OMP.Subset_GOslim_20210509.pdf", GO.OMP.subset, width = 28, height = 28, units = c("in"))



## HI
# Subset and plot only 'other molecular function' (OMF)
go.slim.HI.OMF.subset <- go.HI.subset %>% filter(GO.Slim.Term=="other molecular function")

GO.HI.OMF.subset <- ggplot(go.slim.HI.OMF.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.HI.OMF.subset
ggsave("Output/Figs/HI_OMF.Subset_GOslim_20211011.pdf", GO.HI.OMF.subset, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/OMF.Subset_GOslim_20211011.jpeg", GO.HI.OMF.subset, width = 28, height = 28, units = c("in"))

# Subset and plot only 'other metabolic processes' (OMP)
go.slim.HI.OMP.subset <- go.HI.subset %>% filter(GO.Slim.Term=="other metabolic processes")

GO.HI.OMP.subset <- ggplot(go.slim.HI.OMP.subset, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.HI.OMP.subset
ggsave("Output/Figs/HI_OMP.Subset_GOslim_20211011.pdf", GO.HI.OMP.subset, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/OMP.Subset_GOslim_20210509.pdf", GO.OMP.subset, width = 28, height = 28, units = c("in"))
```

### Because Pdam and Mcav have a GO term in common, I'm going to make a BP GO slim plot to show that overlap
```{r}
## Bind mcav and pdam species dfs together for GO slim plot 
mcav.pdam.go.slim <- rbind(Gene.GO.IDs.slims.mcav, Gene.GO.IDs.slims.pdam)

# Subset and plot by BP
go.slim.Mcav_Pdam.BP <- mcav.pdam.go.slim %>% filter(ontology=="BP")

GO.subset.Mcav_Pdam.BP <- ggplot(go.slim.Mcav_Pdam.BP, aes(x = Species, y = term)) + 
  geom_tile(aes(fill =over_represented_pvalue)) + 
  facet_grid(GO.Slim.Term ~ ., scales = "free_y", labeller = label_wrap_gen(width = 5, multi_line = TRUE))+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),
                     strip.text.y = element_text(angle=0, size = 25),
                     strip.text.x = element_text(size = 25),
                     axis.text = element_text(size = 30))
GO.subset.Mcav_Pdam.BP
ggsave("Output/Figs/Mcav.Pdam_BP_GOslim_20211011.pdf", GO.subset.Mcav_Pdam.BP, width = 28, height = 28, units = c("in"))
#ggsave("~/Desktop/PutnamLab/Repositories/SedimentStress/SedimentStress/Output/Figs/BP_GOslim_20210705.jpeg", GO.subset.Mcav_Pdam.BP, width = 28, height = 28, units = c("in"))
```




